Modelling Stochastic Time Delay Structures for Regression

### 2021-02-14 documentation/article/article.tex
Rewording.
Fix typo
Wording change

where $X(t + T)$ is the time shifted series and $X(t)$ is the observed input.\\

@@

In the univariate case, the utility of the described method is limited. However, we propose three extensions as future work. The first is to extend the method to multivariate regression. We believe that the extension can be built on the same fundamental ideas presented in this document. Next, the model could be extended to include distributed lag structures. A distributed lag structure is where past values of the impulse influence future values of the output. Finally, in relating $x(t)$ to $f(x(t))$, the function f could be extended to the modelling of non-linear forms.

@@

In addition, by incorporating these elements we could begin to explore alternative forms of time series prediction. Essentially, existing prediction mechanisms predict the average across time shifts. In some situations, the predictions resulting from these models could be considered nonsensical.

>>>>

where $X(t + \mathcal{T})$ is the matrix of time shifted impulses and $X(t)$ is the observed input.\\

@@

In the univariate case, the utility of the described method is limited. However, we propose three extensions as future work. The first is to extend the method to multiple regression. We believe that the extension can be built on the same fundamental ideas presented in this document. Next, the model could be extended to include distributed lag structures. A distributed lag structure is where past values of the impulse influence future values of the output. Finally, in relating $x(t)$ to $f(x(t))$, the function f could be extended to the modelling of non-linear forms.

@@

In addition, by incorporating these elements we could begin to explore alternative forms of time series prediction. Essentially, existing prediction mechanisms predict the average across time shifts.However in some situations, the predictions could be considered nonsensical.
